### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@e0808783ac9d706a03a77dd6910f4ab87ccee32b 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@d15303db9a2596862c7e41f1f2d7d05fdc67cbc2 🚀

We have phylogenies and species distributions models.

\begin{figure}
\centering
\includegraphics{./figures/trees.png}
\caption{Phylogeny for both bumblebee species (left) and flower species
(right)}
\end{figure}

\begin{figure}
\centering
\includegraphics{./figures/sample_sdm.png}
\caption{Example SDM for \emph{Archillea millefolium}}
\end{figure}

Transition to next chapter by discussing uncertainty in interaction
prediction across space.

@@

This chapter uses simulation models to investigate the relationship
between species relative abundance, sampling effort, and probability of
accurately detecting an interaction between species, and further
proposes a method for optimizing the spatial sampling locations to
maximize the probability of detecting an interaction between two species
given their distributions. This addresses the optimization of monitoring
network part of the flow from data to mitigation at the top of
fig.~\ref{fig:thesis}, left.

As explored in the previous chapter, there are false-negatives in
interaction data. However, there is more than one way to observe a
false-negative when sampling interactions (fig.~\ref{fig:fnrtaxonomy}).
It begins with a conceptual framework for understanding the difference
in false-negatives in occurrence, co-occurrence, and interactions.
Co-occurrence is not the same thing as interaction (Blanchet \emph{et
al.} 2020), but often is used as a proxy.

@@

We use a log-normal distribution as a null model of the
relative-abundance distribution (Hubbell 2001) and then simulate
realized false-negative rate as a function of varying sampling effort.

This also goes on to includes testing some assumptions of the model with
empirical data fig.~\ref{fig:posassoc}, which we analytically show that
our neutral model, if anything, underestimates the probability of
false-negatives due to positive correlations in co-occurrence in two
sets of spatially replicated samples of interaction networks (Thompson
\& Townsend 2000; Hadfield \emph{et al.} 2014)---further I'm planning to
add the field data from the previous chapter into this anlysis once
available.

\begin{figure}
\hypertarget{fig:posassoc}{%
\centering
\includegraphics{./figures/positiveassociations.png}
\caption{f}\label{fig:posassoc}
}
\end{figure}

Finally this chapter proposes a simulated annealing method to optimize
the efficacy of interaction detection given a set of observation points
where the dist from observation site decays. optimize set of repeated
sampling locations L for a pair of species \emph{known} distributions
\(D_a, D_b\).

>>>>

Here we show the in-progress work on the prerequisites for the analysis
outlined above: phylogenies for both plant and bee species
(fig.~\ref{fig:phylo}) and species distribution models for all species
(an example shown in fig.~\ref{fig:example_sdm}).

\begin{figure}
\hypertarget{fig:phylo}{%
\centering
\includegraphics{./figures/trees.png}
\caption{Phylogeny for both bumblebee species (left) and flower species
(right)}\label{fig:phylo}
}
\end{figure}

\begin{figure}
\hypertarget{fig:example_sdm}{%
\centering
\includegraphics{./figures/sample_sdm.png}
\caption{Example SDM for \emph{Archillea
millefolium}}\label{fig:example_sdm}
}
\end{figure}

@@

This chapter uses simulation models to investigate the relationship
between species relative abundance, sampling effort, and probability of
accurately detecting an interaction between species, and further
proposes a method for optimizing the spatial sampling locations to
maximize the probability of detecting an interaction between two species
given their distributions. This addresses the optimization of monitoring
network part of the flow from data to mitigation at the top of
fig.~\ref{fig:thesis}, left. As explored in the previous chapter, there
are false-negatives in interaction data. However, there is more than one
way to observe a false-negative when sampling interactions.
fig.~\ref{fig:fnrtaxonomy} shows a taxonomy of false-negatives in
occurrence, co-occurrence, and interaction data.

Co-occurrence is not the same thing as interaction (Blanchet \emph{et
al.} 2020), but often is used as a proxy.

@@

The first result is using a log-normal distribution of relative
abundance (Hubbell 2001) to compute a null expectation of the number of
total observations of individuals of \emph{any species} by simulating
the process of observation on food-webs generated using the niche model
(\textbf{williamsmart?}) with connectance parameterized by the
flexible-links model (\textbf{cite?}). An example of this relation for
networks with varying spceies richness is shown in fig.~\ref{fig:fnr}.

\begin{figure}
\hypertarget{fig:fnr}{%
\centering
\includegraphics{./figures/ch2_fnr.png}
\caption{foo}\label{fig:fnr}
}
\end{figure}

We then go on to testing some assumptions of this neutral model with
empirical data. Primarily that we analytically show that our neutral
model, if anything, underestimates the probability of false-negatives if
there are positive associations between species co-occurrence, which we
show exist in two sets of spatially replicated samples of interaction
networks (Thompson \& Townsend 2000; Hadfield \emph{et al.} 2014),
fig.~\ref{fig:posassoc}---further I'm planning to add the field data
from the previous chapter into this analysis once available.

\begin{figure}
\hypertarget{fig:posassoc}{%
\centering
\includegraphics{./figures/positiveassociations.png}
\caption{Demonstrates positive associations in
co-occurrence}\label{fig:posassoc}
}
\end{figure}

Finally this chapter proposes a simulated annealing method to optimize
the efficacy of interaction detection given a set of observation
locations for a pair of species \emph{known} distributions \(D_a, D_b\).
